---
title: ""
subtitle: ""
author: 
  - Shaotong (Max) Li
thanks: "Code and data are available at: [Sakura_Florescence_Prediction](https://github.com/ShaotongLi-Max/Sakura_Florescence_Prediction.git)."
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

#### Workspace setup ####

# Load libraries
library(tidyverse)
library(arrow)
library(here)
library(ggplot2)
library(patchwork)
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggthemes)
library(dplyr)
library(knitr)
library(kableExtra)

# Load cleaned datasets
sakura_historical_cleaned <- read_csv(here::here("data/03-cleaned_data/sakura-historical-cleaned.csv"))
sakura_modern_cleaned <- read_csv(here::here("data/03-cleaned_data/sakura-modern-cleaned.csv"))
# Load temp_test_data for Model 1
temp_test_data <- read_parquet(here::here("data/02-analysis_data/temp_test_data.parquet"))
# Load latitude&time_test_data for Model 2
latitude_time_test_data <- read_parquet(here::here("data/02-analysis_data/latitude&time_test_data.parquet"))
# Load Model 1
model1 <- readRDS(here::here("models/model1.rds"))
# Load Model 2
model2 <- readRDS(here::here("models/model2.rds"))
```

# Introduction

# Data

## Overview

## Measurement

## Outcome Variables

### Florescence

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Combine and Prepare Data ####
# Prepare sakura_historical_cleaned data
historical_flower_data <- sakura_historical_cleaned %>%
  select(flower_doy) %>%
  filter(!is.na(flower_doy)) %>%  # Remove missing values
  mutate(dataset = "Historical")  # Add label for distinction

# Prepare sakura_modern_cleaned data
modern_flower_data <- sakura_modern_cleaned %>%
  select(flower_doy) %>%
  filter(!is.na(flower_doy)) %>%  # Remove missing values
  mutate(dataset = "Modern")  # Add label for distinction

# Combine the datasets
combined_flower_data <- bind_rows(historical_flower_data, modern_flower_data)

#### Plot Flowering Day Distribution ####
flower_doy_distribution_plot <- combined_flower_data %>%
  ggplot(aes(x = flower_doy, fill = dataset, color = dataset)) +
  geom_density(alpha = 0.3, adjust = 1.5) +  # Use density plot for smoother curves
  labs(
    title = "Flowering Day Distribution: Historical vs Modern Data",
    x = "Flowering Day (DOY)",
    y = "Density",
    fill = "Dataset",
    color = "Dataset"
  ) +
  scale_fill_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  scale_color_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.position = "right"
  )

# Display the plot
print(flower_doy_distribution_plot)

```

## Predictor Variables

### Temperature

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Combine and Prepare Data ####
# Prepare sakura_historical_cleaned data
historical_temp_data <- sakura_historical_cleaned %>%
  select(temp) %>%
  filter(!is.na(temp)) %>%  # Remove missing values
  mutate(dataset = "Historical", variable = "temp")  # Add labels for distinction

# Prepare sakura_modern_cleaned data
modern_temp_data <- sakura_modern_cleaned %>%
  select(mean_temp_month) %>%
  filter(!is.na(mean_temp_month)) %>%  # Remove missing values
  rename(temp = mean_temp_month) %>%  # Rename column to match for combining
  mutate(dataset = "Modern", variable = "mean_temp_month")  # Add labels for distinction

# Combine the datasets
combined_temp_data <- bind_rows(historical_temp_data, modern_temp_data)

#### Plot Temperature Distribution ####
temp_distribution_plot <- combined_temp_data %>%
  ggplot(aes(x = temp, fill = dataset, color = dataset)) +
  geom_density(alpha = 0.3, adjust = 1.5) +  # Use density plot for smoother curves
  labs(
    title = "Temperature Distribution: Historical vs Modern Data",
    x = "Temperature (°C)",
    y = "Density",
    fill = "Dataset",
    color = "Dataset"
  ) +
  scale_fill_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  scale_color_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.position = "right"
  )

# Display the plot
print(temp_distribution_plot)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Prepare Data ####
# sakura_historical is already loaded
scatter_data <- sakura_historical_cleaned %>%
  filter(!is.na(temp), !is.na(flower_doy))  # Ensure no missing values

#### Create Scatter Plot ####
scatter_plot_no_line <- ggplot(scatter_data, aes(x = temp, y = flower_doy)) +
  geom_point(aes(color = year), alpha = 0.6, size = 2) +  # Scatter points colored by year
  scale_color_viridis_c(option = "C", name = "Year") +  # Color scale for year
  labs(
    title = "Relationship Between Temperature and Flowering Day",
    subtitle = "Color represents temporal progression",
    x = "Temperature (°C)",
    y = "Flowering Day (DOY)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

# Display the plot
print(scatter_plot_no_line)

```

### Latitude

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Improved Plot Latitude and Longitude Distributions ####

# Plot latitude distribution with bins
latitude_plot <- ggplot(sakura_modern_cleaned, aes(x = latitude)) +
  geom_histogram(
    bins = 20,                    # Adjust the number of bins for better grouping
    fill = "steelblue", 
    alpha = 0.8
  ) +
  labs(
    title = "Latitude Distribution",
    x = "Latitude",
    y = "Count"
  ) +
  theme_minimal()

latitude_plot

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Prepare Latitude Data ####
latitude_temp_data <- sakura_modern_cleaned %>%
  filter(!is.na(latitude), !is.na(mean_temp_month)) %>%
  group_by(latitude) %>%
  summarise(mean_temp = mean(mean_temp_month, na.rm = TRUE)) %>%
  ungroup()

#### Fit a Linear Model ####
linear_model <- lm(mean_temp ~ latitude, data = latitude_temp_data)

#### Create Plot ####
latitude_temp_plot <- ggplot(latitude_temp_data, aes(x = latitude, y = mean_temp)) +
  geom_line(color = "steelblue", size = 1) +  # Line graph with custom color and size
  geom_abline(
    slope = coef(linear_model)["latitude"],
    intercept = coef(linear_model)["(Intercept)"],
    color = "darkorange",
    linetype = "dashed",
    size = 1
  ) +  # Add a dashed line for the linear relationship
  labs(
    title = "Mean Temperature by Latitude",
    subtitle = "Relationship between Latitude and Mean Temperature with Linear Trend",
    x = "Latitude",
    y = "Mean Temperature (°C)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

# Display the plot
print(latitude_temp_plot)


```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Load and Prepare Data ####
# Calculate mean temperature for each location
temperature_summary <- sakura_modern_cleaned %>%
  group_by(latitude, longitude) %>%
  summarise(mean_temp_month = mean(mean_temp_month, na.rm = TRUE)) %>%
  ungroup()

#### Load Japan's Basemap ####
japan_map <- ne_countries(scale = "medium", country = "Japan", returnclass = "sf")

#### Create the Map for Temperature ####
gis_plot_temp <- ggplot(data = japan_map) +
  geom_sf(fill = "white", color = "black") +  # Base map of Japan
  geom_point(
    data = temperature_summary,
    aes(x = longitude, y = latitude, color = mean_temp_month),
    size = 3, alpha = 0.7
  ) +
  scale_color_gradientn(
    colors = c("#2c7bb6", "#abd9e9", "#ffffbf", "#fdae61", "#d7191c"),  # Blue to red gradient
    name = "Mean Temperature (°C)"
  ) +
  theme_minimal() +
  labs(
    title = "Average Monthly Temperatures Across Japan",
    subtitle = "Warmer colors indicate higher temperatures",
    x = "Longitude",
    y = "Latitude"
  ) +
  theme(legend.position = "right")

# Display the plot
print(gis_plot_temp)

```

### Time of Blossom

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Plot Monthly Distribution of Flower Date ####

# Extract the month from flower_date and create a summary table
flower_month_distribution <- sakura_modern_cleaned %>%
  mutate(month = month(flower_date, label = TRUE, abbr = TRUE)) %>%  # Extract abbreviated month names
  count(month)  # Count the occurrences for each month

# Plot the monthly distribution
flower_month_plot <- ggplot(flower_month_distribution, aes(x = month, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue", alpha = 0.8) +  # Use steelblue for the bars
  labs(
    title = "Monthly Distribution of Flower Date",
    x = "Month",
    y = "Count"
  ) +
  theme_minimal()

# Display the plot
flower_month_plot
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Plot Distribution of Flower Dates by Month and Day ####

# Extract month and day from flower_date
flower_date_distribution <- sakura_modern_cleaned %>%
  mutate(month = month(flower_date, label = TRUE, abbr = TRUE),  # Extract abbreviated month names
         day = day(flower_date))  # Extract day of the month

# Create a summarized dataset for the count of flower dates by month and day
flower_date_summary <- flower_date_distribution %>%
  group_by(month, day) %>%
  summarise(count = n(), .groups = "drop")

# Use a broader color palette for all months
color_palette <- scales::hue_pal()(length(unique(flower_date_summary$month)))

# Plot the line graph
flower_date_line_plot <- ggplot(flower_date_summary, aes(x = day, y = count, color = month, group = month)) +
  geom_line(size = 1) +  # Draw smooth lines for each month
  scale_color_manual(values = color_palette) +  # Use a color palette for all months
  labs(
    title = "Flower Date Distribution by Month and Day",
    x = "Day of the Month",
    y = "Count",
    color = "Month"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right"
  )

# Display the plot
flower_date_line_plot
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Plot Distribution of Temperature by Date ####

# Extract date and temperature from the dataset
temperature_distribution <- sakura_modern_cleaned %>%
  select(flower_date, mean_temp_month) %>%
  mutate(
    day_of_year = yday(flower_date),  # Convert date to day of the year
    month = month(flower_date, label = TRUE, abbr = TRUE)  # Extract month for potential color coding
  )

# Create the plot
temperature_plot <- ggplot(temperature_distribution, aes(x = day_of_year, y = mean_temp_month)) +
  geom_point(alpha = 0.5, color = "steelblue") +  # Scatter plot of temperature
  geom_smooth(method = "loess", color = "darkorange", size = 1, se = FALSE) +  # Smoothed line for trend
  labs(
    title = "Temperature Distribution by Date",
    subtitle = "Scatter plot with temperature trend over the year",
    x = "Day of the Year",
    y = "Temperature (°C)"
  ) +
  scale_x_continuous(
    breaks = c(1, 32, 60, 91, 121, 152),  # Manually specify breaks for Jan, Feb, Mar, Apr, May
    labels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun")  # Correct labels
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

# Display the plot
print(temperature_plot)


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Load and Prepare Data ####
# Calculate mean flower_doy for each location
sakura_summary <- sakura_modern_cleaned %>%
  group_by(latitude, longitude) %>%
  summarise(mean_flower_doy = mean(flower_doy, na.rm = TRUE)) %>%
  ungroup()

#### Load Japan's Basemap ####
japan_map <- ne_countries(scale = "medium", country = "Japan", returnclass = "sf")

#### Create the Map ####
gis_plot <- ggplot(data = japan_map) +
  geom_sf(fill = "white", color = "black") +  # Base map of Japan
  geom_point(
    data = sakura_summary,
    aes(x = longitude, y = latitude, color = mean_flower_doy),
    size = 3, alpha = 0.7
  ) +
  scale_color_viridis_c(
    option = "D",  # Viridis color scale for better visualization
    name = "Mean Flower DOY"
  ) +
  theme_minimal() +
  labs(
    title = "Average Flowering Dates Across Japan",
    subtitle = "Darker points indicate later flowering dates",
    x = "Longitude",
    y = "Latitude"
  ) +
  theme(legend.position = "right")

# Display the plot
print(gis_plot)
```
## Excluded Variables

### Year

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Prepare Data ####
# sakura_historical_cleaned is already loaded
line_data <- sakura_historical_cleaned %>%
  filter(!is.na(temp), !is.na(year))  # Ensure no missing values

# Calculate mean temperature to use as a horizontal reference line
mean_temp <- mean(line_data$temp, na.rm = TRUE)

#### Create Line Plot ####
line_plot <- ggplot(line_data, aes(x = year, y = temp)) +
  geom_line(color = "steelblue", size = 1) +  # Line graph with color and size
  geom_hline(
    yintercept = mean_temp, 
    color = "darkorange", 
    linetype = "dashed", 
    size = 1
  ) +  # Add horizontal dashed line for reference
  labs(
    title = "Temperature Trend Over Years",
    subtitle = "Yearly average temperature with reference line",
    x = "Year",
    y = "Temperature (°C)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

# Display the plot
print(line_plot)

```

### Longitude

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Improved Plot Latitude and Longitude Distributions ####
# Plot longitude distribution with bins
longitude_plot <- ggplot(sakura_modern_cleaned, aes(x = longitude)) +
  geom_histogram(
    bins = 20,                    # Adjust the number of bins for better grouping
    fill = "darkorange", 
    alpha = 0.8
  ) +
  labs(
    title = "Longitude Distribution",
    x = "Longitude",
    y = "Count"
  ) +
  theme_minimal()

# Display the plots
longitude_plot

```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Prepare Longitude Data ####
longitude_temp_data <- sakura_modern_cleaned %>%
  filter(!is.na(longitude), !is.na(mean_temp_month)) %>%
  group_by(longitude) %>%
  summarise(mean_temp = mean(mean_temp_month, na.rm = TRUE)) %>%
  ungroup()

#### Fit a Linear Model ####
linear_model <- lm(mean_temp ~ longitude, data = longitude_temp_data)

#### Create Plot ####
longitude_temp_plot <- ggplot(longitude_temp_data, aes(x = longitude, y = mean_temp)) +
  geom_line(color = "darkorange", size = 1) +  # Line graph with custom color and size
  geom_abline(
    slope = coef(linear_model)["longitude"],
    intercept = coef(linear_model)["(Intercept)"],
    color = "steelblue",
    linetype = "dashed",
    size = 1
  ) +  # Add a dashed line for the linear relationship
  labs(
    title = "Mean Temperature by Longitude",
    subtitle = "Relationship between Longitude and Mean Temperature with Linear Trend",
    x = "Longitude",
    y = "Mean Temperature (°C)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

# Display the plot
print(longitude_temp_plot)

```

# Model

## Alternative Model 

```{=tex}
\begin{equation}
\text{Alternative Model: } \text{mean\_temp\_month} = \beta_1 \cdot \text{latitude} + \beta_2 \cdot \text{longitude} + \beta_0
\end{equation}

\noindent
where:
\begin{itemize}
    \item $\text{latitude} \in [20, 50]$, representing geographical latitude in degrees (°N).
    \item $\text{longitude} \in [120, 150]$, representing geographical longitude in degrees (°E).
    \item $\beta_1$ and $\beta_2$ are coefficients for $\text{latitude}$ and $\text{longitude}$, respectively.
    \item $\beta_0$ is the intercept term.
    \item Both $\text{latitude}$ and $\text{longitude}$ are numerical variables.
\end{itemize}
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Create a data frame for the coefficients and p-values
summary_table <- data.frame(
  Variable = c("latitude", "longitude"),
  Estimate = c(0.778101, -0.003319),
  P_Value = c("<2e-16", "0.806")
)

# Add R-squared information to the table
r_squared <- 0.6722
adjusted_r_squared <- 0.6721

# Combine R-squared information into the table
model_info <- data.frame(
  Variable = c("R-squared", "Adjusted R-squared"),
  Estimate = c(r_squared, adjusted_r_squared),
  P_Value = c("", "") # No p-value for R-squared metrics
)

# Combine both tables
final_table <- rbind(summary_table, model_info)

# Beautify the final_table using kable
kable(
  final_table,
  format = "latex",             # Output in LaTeX format
  booktabs = TRUE,              # Use booktabs style for clean table
  align = "c",                  # Center align columns
  col.names = c("Variable", "Estimate", "P-Value") # Column names
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"), # Add striped rows and fixed position
    full_width = FALSE                             # Keep the table compact
  ) %>%
  add_header_above(c(" " = 1, "Model Summary" = 2)) # Add a header spanning the last two columns
```

## Model 1

```{=tex}
\begin{equation}
\text{Model 1: } \text{flower\_doy} = \beta_1 \cdot \text{temp} + \beta_0
\end{equation}

\noindent
where:
\begin{itemize}
    \item $\text{temp} \in [1, 12]$, representing the temperature range in degrees Celsius (°C).
    \item $\beta_1$ is the coefficient of the variable $\text{temp}$, and $\beta_0$ is the intercept term.
    \item The variable $\text{temp}$ is a numerical variable.
\end{itemize}
```

## Model 2

```{=tex}
\begin{equation}
\text{Model 2: } \text{mean\_temp\_month} = \beta_1 \cdot \text{day} + \beta_2 \cdot \text{latitude} + \beta_3 \cdot \text{month} + \beta_0
\end{equation}

\noindent
where:
\begin{itemize}
    \item $\text{latitude} \in [20, 50]$, representing geographical latitude in degrees (°N).
    \item $\text{day} \in [1, 31]$, representing the day of the month.
    \item $\text{month}$ is a categorical variable representing months (January to May).
    \item $\beta_1$, $\beta_2$, $\beta_3$ are coefficients of the linear model, and $\beta_0$ is the intercept term.
    \item All variables are numerical variables, except for $\text{month}$, which is a categorical variable.
\end{itemize}
```

# Result

## Model Result

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Preprocess Test Data for Model 2 ####
# Ensure necessary columns are present for Model 2
latitude_time_test_data <- latitude_time_test_data %>%
  mutate(
    month = factor(month(flower_date)),  # Convert month to a factor (categorical variable)
    day = day(flower_date)              # Extract the day from the flower_date
  )

#### Predictions ####
# Predict using Model 1
temp_test_data <- temp_test_data %>%
  mutate(predicted_flower_doy = predict(model1, newdata = temp_test_data))

# Predict using Model 2
latitude_time_test_data <- latitude_time_test_data %>%
  mutate(predicted_mean_temp_month = predict(model2, newdata = latitude_time_test_data))

#### Plot Results ####
# Plot for Model 1: Actual vs Predicted Flower DOY
plot_model1 <- ggplot(temp_test_data, aes(x = flower_doy, y = predicted_flower_doy)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_abline(slope = 1, intercept = 0, color = "darkorange", linetype = "dashed") +
  labs(
    title = "Model 1: Actual vs Predicted Flower DOY",
    subtitle = "Prediction accuracy for flower day using temperature data",
    x = "Actual Flower DOY",
    y = "Predicted Flower DOY"
  ) +
  theme_minimal()

# Plot for Model 2: Actual vs Predicted Mean Temperature
plot_model2 <- ggplot(latitude_time_test_data, aes(x = mean_temp_month, y = predicted_mean_temp_month)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_abline(slope = 1, intercept = 0, color = "darkorange", linetype = "dashed") +
  labs(
    title = "Model 2: Actual vs Predicted Mean Temperature",
    subtitle = "Prediction accuracy for mean temperature using latitude & time data",
    x = "Actual Mean Temperature (°C)",
    y = "Predicted Mean Temperature (°C)"
  ) +
  theme_minimal()

# Display the plots
print(plot_model1)
print(plot_model2)
```

## Example of Prediction

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Define Real Data Point ####
real_data <- tibble(
  year = 1969,
  flower_date = as.Date("1969-04-29"),
  flower_doy = 119,
  station_name = "Esashi",
  mean_temp_month = 3.9,
  latitude = 40.82,
  longitude = 140.77
)

#### Prepare Data for Model 2 ####
# Add derived variables: month and day
real_data <- real_data %>%
  mutate(
    month = factor(month(flower_date)),  # Convert month to categorical variable
    day = day(flower_date)              # Extract day of the month
  )

#### Predict Temperature using Model 2 ####
predicted_mean_temp <- predict(model2, newdata = real_data)

#### Prepare Data for Model 1 ####
# Create a new data frame for Model 1 with the predicted temperature
real_data_model1 <- real_data %>%
  mutate(temp = predicted_mean_temp)  # Add predicted temperature as 'temp'

#### Predict Flower DOY using Model 1 ####
predicted_flower_doy <- predict(model1, newdata = real_data_model1)

#### Combine Results ####
comparison <- tibble(
  Metric = c("Mean Temperature (°C)", "Flower DOY"),
  Actual = c(real_data$mean_temp_month, real_data$flower_doy),
  Predicted = c(predicted_mean_temp, predicted_flower_doy)
)

#### Beautify the comparison table using kable ####
comparison %>%
  kable(
    format = "latex",            # Output in LaTeX format
    booktabs = TRUE,             # Use booktabs style for clean table
    align = "c",                 # Center align columns
    col.names = c("Metric", "Actual", "Predicted")  # Column names
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),  # Add striped rows and fixed position
    full_width = FALSE                              # Keep the table compact
  ) %>%
  add_header_above(c(" " = 1, "Prediction Summary" = 2))  # Add a header spanning last two columns

```

# Discussion

## Limitation

## Interpretation and Future Research Directions

# Appendix

## Survey Methodology Overview

## Idealized Survey

## Model Details

\newpage

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Create a data frame for residuals
residuals_table <- data.frame(
  Statistic = c("Min", "1Q", "Median", "3Q", "Max"),
  Value = c(-0.25208, -0.14651, -0.04095, 0.04606, 1.30709)
)

# Create a data frame for coefficients
coefficients_table <- data.frame(
  Variable = c("(Intercept)", "temp"),
  Estimate = c(126.202188, -3.509279),
  Std_Error = c(0.034396, 0.005355),
  T_value = c(3669.1, -655.3),
  P_Value = c("<2e-16", "<2e-16")
)

# Create a data frame for model summary
model_summary_table <- data.frame(
  Metric = c(
    "Residual Standard Error", 
    "Multiple R-squared", 
    "Adjusted R-squared", 
    "F-statistic", 
    "P-value"
  ),
  Value = c(
    "0.2337 on 572 degrees of freedom",
    "0.9987",
    "0.9987",
    "4.294e+05 on 1 and 572 DF",
    "<2e-16"
  )
)

# Residuals Table for Model 1
cat("\nResiduals for Model 1:\n")
kable(
  residuals_table, 
  format = "latex", 
  booktabs = TRUE, 
  align = "c"
) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c("Residuals for Model 1" = 2)) 

# Coefficients Table for Model 1
cat("\nCoefficients for Model 1:\n")
kable(
  coefficients_table, 
  format = "latex", 
  booktabs = TRUE, 
  align = "c",
  col.names = c("Variable", "Estimate", "Std. Error", "t Value", "P-Value")
) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c("Coefficients for Model 1" = 5)) 

# Model Summary Table for Model 1
cat("\nModel Summary for Model 1:\n")
kable(
  model_summary_table, 
  format = "latex", 
  booktabs = TRUE, 
  align = "c",
  col.names = c("Metric", "Value")
) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c("Model Summary for Model 1" = 2)) 

```

\newpage

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load necessary library
library(knitr)
library(kableExtra)

# Create a data frame for residuals
residuals_table <- data.frame(
  Statistic = c("Min", "1Q", "Median", "3Q", "Max"),
  Value = c(-4.2185, -0.6993, -0.0729, 0.6641, 4.1114)
)

# Create a data frame for coefficients
coefficients_table <- data.frame(
  Variable = c("(Intercept)", "day", "latitude", "month2", "month3", "month4", "month5"),
  Estimate = c(-9.000439, -0.049223, 0.189083, -0.617982, 2.869383, 6.966108, 10.047363),
  Std_Error = c(0.289464, 0.003291, 0.012089, 0.219831, 0.114364, 0.164984, 0.237453),
  T_value = c(-31.093, -14.956, 15.637, -2.811, 25.088, 42.223, 42.313),
  P_Value = c("<2e-16", "<2e-16", "<2e-16", "0.00496", "<2e-16", "<2e-16", "<2e-16")
)

# Create a data frame for model summary
model_summary_table <- data.frame(
  Metric = c(
    "Residual Standard Error", 
    "Multiple R-squared", 
    "Adjusted R-squared", 
    "F-statistic", 
    "P-value"
  ),
  Value = c(
    "1.116 on 4256 degrees of freedom",
    "0.9255",
    "0.9254",
    "8814 on 6 and 4256 DF",
    "<2e-16"
  )
)

# Residuals Table
cat("\nResiduals for Model 2:\n")
kable(
  residuals_table, 
  format = "latex", 
  booktabs = TRUE, 
  align = "c"
) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c("Residuals for Model 2" = 2)) 

# Coefficients Table
cat("\nCoefficients for Model 2:\n")
kable(
  coefficients_table, 
  format = "latex", 
  booktabs = TRUE, 
  align = "c",
  col.names = c("Variable", "Estimate", "Std. Error", "t Value", "P-Value")
) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c("Coefficients for Model 2" = 5)) 

# Model Summary Table
cat("\nModel Summary for Model 2:\n")
kable(
  model_summary_table, 
  format = "latex", 
  booktabs = TRUE, 
  align = "c",
  col.names = c("Metric", "Value")
) %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c("Model Summary for Model 2" = 2)) 

```
